A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters via Convex Optimization

### 2017-02-15 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft/Draft.tex
updated files

%===============================================================================
\section{Introduction}
Today's industrial processes pose challenging problems to control engineers due to the increasing complexities of system structures. In order to simplify the controller design process, these systems are approximated with low-order models; this reduces both time and effort in synthesizing a controller. However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty. Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant). A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement noise.

@@

The proposed method in this paper invokes a new data-driven control design scheme for a specific power converter application at CERN. Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry). In fact, the authors in \cite{NW95} assert that even small deformations in the beam pipe can drastically change the impedance of the system and create stability issues. Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.  In this work, it is shown that a loop-shaping design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions). Additionally, with certain trivial conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.

@@

\section{System Framework}
\label{sec:system}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/circuit_partial_a}
\caption{Power converter filter schematic (from $v_i$ to $v_0$). The magnet represents the load of the process.}
\label{fig:circuit}
\end{figure}
The power converter voltage source filter has the structure shown in Fig.~\ref{fig:circuit}. The input voltage $v_i$ is the output of a pulse-width modulated signal (which will be discussed in more detail in section \ref{sec:case}). The TF from $v_i$ to $v_0$ describes the filter of the power converter. The magnet (i.e., the load) is connected to the output of the converter. For general applications at CERN, the objective is to control the current in the magnet (through $L_m$) such that the error between this output current and a delayed version of the reference current is minimized. However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$. This intermediate control is performed due to the fact that the power converter typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop. Another reason for implementing this type of control structure at CERN is for commissioning purposes; if/when faults occur in the system, each loop can be verified one at a time to ensure quality operation.

The system structure for this application is shown in Fig.~\ref{fig:damping_loop}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/damping_loop_full}
\caption{Interconnection of the power converter control system. }
\label{fig:damping_loop}
\end{figure}
$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$). From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action. For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$. The objective of this application is to design controllers such the TF from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
G_d(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
\end{aligned}
\end{equation}
where $k \in \{k_i,k_u,k_{m_1},k_{m_2}\}$. Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$.  Then these closed-loop TF's can easily be derived as follows:

\begin{align}
T^{\prime}(s,k) &= \frac{G_d(s)(1+k_u)}{1+G_d(s)[H_1(s,k)+H_2(s,k)]} \label{eq:Tclp}  \\ 
T(s,k) &= \frac{G_d(s)[1+k_u+C_m(s,k)]}{1+G_d(s)[H_1(s,k)+H_2(s,k)+C_m(s,k)]}  \label{eq:Tcl} 
\end{align}

@@

\subsection{Convex Approximation}
The type of optimization problem that will be considered in this paper will have the following form:

@@

The control methodology in this paper is based on minimizing a control objective in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense. In subsequent sections, it will be shown that these performance constraints will have the following quadratic form:

@@

\subsection{Control Performance}
Since the control methods discussed in this paper are based on the $\mathcal{H}_\lambda$ criterion ($\lambda \in \{2,\infty \}$), it is appropriate to first define this criterion in the context of this work. A typical control objective is to design a controller such that the following constraint is satisfied:
\begin{equation} \label{eq:WS_lt1}
\| W_q \mathcal{S}_q\| < 1
\end{equation}
where $\mathcal{S}_q$ is the $q$-th sensitivity function of interest, and $W_q$ is a stable weighting function such that $\| W_q \mathcal{S}_q\|$ is bounded. The norm considered in (\ref{eq:WS_lt1}) can be either the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norm.

@@

A loop-shaping criterion can also be considered as a form of control performance. If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the $\mathcal{H}_2$ or $\mathcal{H}_\infty$ sense in order to shape $T$.  The next section will discuss how an optimization problem can be formulated for this type of control methodology.

@@

 \begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[T(k)-T_d\bigr]^{\star}\bigl[T(k)-T_d\bigr] < \gamma
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let $z(k) = 1+G_d[H_1(k)+H_2(k)+C_m(k)]$ and $N(k) = G_d[1+k_u+C_m(k)]$; then the above constraint can be written as:

\begin{equation}
\bigl[N(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[N(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
\end{equation}

@@

\begin{equation} \label{eq:loop_shape_LMI_inf}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \gamma  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[N(k)-z(k)T_d]^{\star} \\ 
N(k)-z(k)T_d & \phantom{xx}\gamma
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$, where $z_0 = 1+G_d[H_1(k_0) + H_2(k_0)+C_m(k_0)]$ and $k_0 \in \{k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  \}$ are the initializing gains. In a similar manner, the following convex optimization problem can be considered for minimizing  $ \|T(k)- T_d \|_2^2$, as follows:

\begin{equation} \label{eq:loop_shape_LMI_2}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \int_0^\infty \gamma(\omega) d\omega  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[N(k)-z(k)T_d]^{\star} \\ 
N(k)-z(k)T_d & \phantom{xx}\gamma(\omega)
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. For this $\mathcal{H}_2$ problem, note that $\gamma$ is now a function of $\omega$ (which contrasts with the optimization problem in the $\mathcal{H}_\infty$ sense).

@@

The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G_d[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = G_dF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+G_dF$ makes $n_{G_d}+n_F$ counter-clockwise encirclements of the origin (where $n_{G_d}$ and $n_F$ are, respectively, the number of RHP poles of $G_d$ and $F$). The Nyquist plot of $1+G_dF$ must also not pass through the origin.

\begin{theorem} \label{Thm1}
Suppose that $k_i$, $k_u$, $k_{m_1}$, and $k_{m_2}$ are feasible solutions to the following constraint:
\begin{equation} \label{eq:theorem1_cond}
\begin{split}
z^{\star}(k)z_0+z_0^{\star}z(k) > 0 \\
\forall \omega \in \Omega
\end{split}
\end{equation}
where 
\begin{align*}
z(k) &= 1+G_d[H_1(k)+H_2(k)+C_m(k)] \\
z_0 &= 1+G_d[H_1(k_0)+H_2(k_0)+C_m(k_0)]
\end{align*}
with $\{G_d,H_1,H_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
\end{theorem}

\textit{Proof:}
The proof is based on the Nyquist stability criterion and the properties of the winding number. The winding number of $z^{\star}(k)z_0$ is given as follows:
\begin{equation} \label{eq:winding_proof}
\begin{aligned}
{\mbox{wno}} \{ z^{\star}(k)z_0\} &= {\mbox{wno}} \{ z^{\star}\} + {\mbox{wno}} \{ z_0\} \\
&= -{\mbox{wno}} \{ 1+G_dF(k)\} \\
&\phantom{=} + {\mbox{wno}} \{ 1+G_dF(k_0)\} \\
\end{aligned}
\end{equation}
where $F(k_0) = H_1(k_0) + H_2(k_0) + C_m(k_0)$. Note that $F(k)$ is strictly proper and $G_dF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour. Additionally, the constraint in (\ref{eq:theorem1_cond}) implies that $\Re\{ z^{\star}(k)z_0\} > 0$ (where $\Re\{ \cdot \}$ indicates the real part of the argument), which signifies that the Nyquist plot of $z^{\star}(k)z_0$ will not pass through or encircle the origin. Therefore, $\mbox{wno} \{ z^{\star}(k)z_0\} = 0$; from (\ref{eq:winding_proof}), the following condition can then be realized:
\begin{equation} \label{eq:winding_proof3}
\mbox{wno} \{ 1+G_dF(k)\} = {\mbox{wno}} \{ 1+G_dF(k_0)\}
\end{equation}
The condition in (\ref{eq:winding_proof3}) implies that if the initializing controllers $k_0$ are stabilizing (i.e., the open-loop system $G_dF(k_0)$ meets the Nyquist stability criterion), then the closed-loop system will be stable.
{\hfill \ensuremath{\blacksquare}}

\subsection{Initializing Controller}
For the given structure in Figure.~\ref{fig:damping_loop}, it remains to show how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system. From the control structure of the power converter control system, it can be observed that if all the gains in Figure.~\ref{fig:damping_loop} are set to zero, then the system will be in open-loop. However, since $G_d \in \mathscr{S}$, then selecting $k_0 = 0$ will guarentee the stability of the closed-loop system.

If the initializing controllers are selected such that the performance with these controllers is far from the desired performance, then it is possible that either the optimization problem yields no feasible solution, or that the solver runs into numerical problems (which leads to infeasible solutions). One method to resolve this problem is to apply relaxation techniques where a relaxed optimization problem is solved; the solution to the relaxed problem is then used as the initializing controllers for the non-relaxed problem.

\subsection{Convex Optimization via Semi-Definite Programming}
All of the optimization problems considered in section \ref{sec:loop_shape} are known as semi-infinite programming (SIP) problems since there are a finite number of optimization variables $k$ and an infinite number of constraints with respect to $\omega$. To solve any of these problems, the optimization algorithm can be converted to a semi-definite programming (SDP) problem. In this manner, a predefined frequency grid can be implemented in order to solve a finite number of constraints. In other words, for a finite number of frequency points $n$ selected in $\omega \in [0,\infty)$, then $n$ constraints must be satisfied. This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}, \cite{FR05}).

@@

@@

\subsection{Frequency Response Measurement}
Since the proposed method uses a data-driven methodology with frequency-domain data, the FRF of each subsystem within the power converter control system must be obtained. In other words, we must obtain the FRF of $G_d$, $H$, $P_1$, and $P_2$. The signals that are accessible for the measurements are the inputs to the capacitor banks ($U_{dc}$ in Fig.~\ref{fig:schematic}, which is approximately equal to $v_r$ in Fig.~\ref{fig:damping_loop}), and the outputs of the sensors $P_1$ and $P_2$. Therefore, when all of the controller gains are set to zero, we are able to obtain the frequency responses of $G_dHP_1$ and $G_dP_2$. However, note that $G_d$ appears independently of $P_2$ in (\ref{eq:Tclp}) and (\ref{eq:Tcl}); since $P_1$ and $P_2$ are sensors with very high bandwidths relative to $G_d$ (approximately $10 \: kHz$), then $G_d \approx G_dP_2$  at frequencies less than $1 \: kHz$.

The frequency response of the subsystems were obtained with a transfer function analyzer (Powertek GP102) which implements a sine-sweep method that recovers the gain and phase of a system at discrete frequency points. The appropriate scaling factors were taken into account for the measurements (due to the series connection of the SATURN modules) in order to coincide with the structure used in Fig.~\ref{fig:damping_loop}. The frequency responses of $G_dP_2$ and $G_dHP_1$ are shown in Fig.~\ref{fig:G} and Fig.~\ref{fig:GHP1}, respectively.

@@

Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment. This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$ (when the system is operating in closed-loop mode). The value of the delay is uncertain and is known to be in the range of $\tau_e \in [0,30]\mu s$. Therefore, a multi-model design can be considered where the additional delay can be gridded in this range and incorporated into the closed-loop TF's. The grid was established in intervals of $5 \: \mu s$ (i.e., $\tau_{e_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).

>>>>

%===============================================================================
\section{Introduction}
Today's industrial processes pose challenging problems to control engineers due to the increasing complexities of system structures. In order to simplify the controller design process, these systems are approximated with low-order models; this reduces both time and effort in synthesizing a controller. However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty. Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant). A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement uncertainty.

@@

The method proposed in this paper invokes a new data-driven control design scheme for specific power converter applications at CERN. Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry). In fact, the authors in \cite{NW95} assert that even small deformations in the beam pipe can drastically change the impedance of the system and create stability issues. Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.  In this work, it is shown that a loop-shaping design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions). Additionally, with certain trivial conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.

@@

\section{System Framework}
\label{sec:system}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/circuit_partial_a}
\caption{Power converter filter schematic (from $v_i$ to $v_0$). The magnet represents the load of the process.}
\label{fig:circuit}
\end{figure}
The power converter voltage source filter has the structure shown in Fig.~\ref{fig:circuit}. The input voltage $v_i$ is the output of a pulse-width modulated system (which will be discussed in more detail in section \ref{sec:case}). The TF from $v_i$ to $v_0$ describes the output filter of the power converter. The magnet (i.e., the load) is connected to the output of the converter. For general applications at CERN, the objective is to control the current in the magnet (through $L_m$) such that the error between this output current and a delayed version of the reference current is minimized. However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$. This intermediate control is performed due to the fact that the output typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop. These large resonances are present because the values of the filter resistances are small (in order to reduce the power losses). Large resistance values can attenuate the resonances at the price of larger power losses. Another reason for implementing this type of control structure at CERN is for commissioning purposes; if/when faults occur in the system, each loop can be verified one at a time to ensure quality operation.

The system structure for this application is shown in Fig.~\ref{fig:damping_loop}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/damping_loop_full}
\caption{Interconnection of the power converter control system. }
\label{fig:damping_loop}
\end{figure}
$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$). From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action. For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$ (where $H$ possesses a zero at zero). The objective of this application is to design controllers such the TFs from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
G(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
\end{aligned}
\end{equation}
where $k = [k_i,k_u,k_{m_1},k_{m_2}]$. Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$. These closed-loop TFs can easily be derived as follows:

\begin{align}
T^{\prime}(s,k) &= \frac{G(s)(1+k_u)}{1+G(s)[H_1(s,k)+H_2(s,k)]} \label{eq:Tclp}  \\ 
T(s,k) &= \frac{G(s)[1+k_u+C_m(s,k)]}{1+G(s)[H_1(s,k)+H_2(s,k)+C_m(s,k)]}  \label{eq:Tcl} 
\end{align}

@@

\subsection{Convex Approximation}
The type of optimization problem that will be considered will have the following form:

@@

The control methodology is based on minimizing a control objective in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense. In subsequent sections, it will be shown that these performance constraints will have the following quadratic form:

@@

\subsection{Control Performance}
Since the control methods discussed in this paper are based on the $\mathcal{H}_\lambda$ criterion ($\lambda \in \{2,\infty \}$), it is appropriate to first define this criterion in the context of this work. A typical control objective is to design a controller such that the following constraint is satisfied:
\begin{equation} \label{eq:WS_lt1}
\| W \mathcal{S}\| < 1
\end{equation}
where $\mathcal{S}$ is the sensitivity function of interest, and $W$ is a stable weighting function such that $\| W \mathcal{S}\|$ is bounded. The norm considered in (\ref{eq:WS_lt1}) can be either the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norm.

@@

A loop-shaping criterion can also be considered as a form of control performance. If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the $\mathcal{H}_2$ or $\mathcal{H}_\infty$ sense in order to shape $T$.  The next section will discuss how such an optimization problem can be formulated for this type of control methodology.

@@

 \begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[T(k)-T_d\bigr]^{\star}\bigl[T(k)-T_d\bigr] < \gamma
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let us now define the following quantities:
\begin{equation} 
\begin{aligned}
w(k) &= G[1+k_u+C_m(k)] \\
z(k) &= 1+G[H_1(k)+H_2(k)+C_m(k)]
\end{aligned}
\end{equation}
where it is evident that $T(k) = w(k)z^{-1}(k)$; then the constraint in (\ref{eq:min_loopshape}) can be written as:

\begin{equation}
\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
\end{equation}

@@

\begin{equation} \label{eq:loop_shape_LMI_inf}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \gamma  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
w(k)-z(k)T_d & \phantom{xx}\gamma
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$, where $z_0 = 1+G[H_1(k_0) + H_2(k_0)+C_m(k_0)]$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains. In a similar manner, the following convex optimization problem can be considered for minimizing  $ \|T(k)- T_d \|_2^2$, as follows:

\begin{equation} \label{eq:loop_shape_LMI_2}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \int_0^\infty \gamma(\omega) d\omega  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
w(k)-z(k)T_d & \phantom{xx}\gamma(\omega)
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. For this $\mathcal{H}_2$ problem, note that $\gamma$ is now a function of $\omega$ (which contrasts with the optimization problem in the $\mathcal{H}_\infty$ sense).

@@

The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+C_m(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of RHP poles of $G$ and $F$). The Nyquist plot of $1+GF$ must also not pass through the origin.

\begin{theorem} \label{Thm1}
Suppose that $k_i$, $k_u$, $k_{m_1}$, and $k_{m_2}$ are feasible solutions to the following constraint:
\begin{equation} \label{eq:theorem1_cond}
\begin{split}
z^{\star}(k)z_0+z_0^{\star}z(k) > 0 \\
\forall \omega \in \Omega
\end{split}
\end{equation}
where 
\begin{align*}
z(k) &= 1+G[H_1(k)+H_2(k)+C_m(k)] \\
z_0 &= 1+G[H_1(k_0)+H_2(k_0)+C_m(k_0)]
\end{align*}
with $\{G,H_1,H_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
\end{theorem}

\textit{Proof:}
The proof is based on the Nyquist stability criterion and the properties of the winding number. The winding number of $z^{\star}(k)z_0$ is given as follows:
\begin{equation} \label{eq:winding_proof}
\begin{aligned}
{\mbox{wno}} \{ z^{\star}(k)z_0\} &= {\mbox{wno}} \{ z^{\star}\} + {\mbox{wno}} \{ z_0\} \\
&= -{\mbox{wno}} \{ 1+GF(k)\} \\
&\phantom{=} + {\mbox{wno}} \{ 1+GF(k_0)\} \\
\end{aligned}
\end{equation}
where $F(k_0) = H_1(k_0) + H_2(k_0) + C_m(k_0)$. Note that $F(k)$ is strictly proper and $GF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour. Additionally, the constraint in (\ref{eq:theorem1_cond}) implies that $\Re\{ z^{\star}(k)z_0\} > 0$ (where $\Re\{ \cdot \}$ indicates the real part of the argument), which signifies that the Nyquist plot of $z^{\star}(k)z_0$ will not pass through or encircle the origin. Therefore, $\mbox{wno} \{ z^{\star}(k)z_0\} = 0$; from (\ref{eq:winding_proof}), the following condition can then be realized:
\begin{equation} \label{eq:winding_proof3}
\mbox{wno} \{ 1+GF(k)\} = {\mbox{wno}} \{ 1+GF(k_0)\}
\end{equation}
The condition in (\ref{eq:winding_proof3}) implies that if the initializing controllers $k_0$ are stabilizing (i.e., the open-loop system $GF(k_0)$ meets the Nyquist stability criterion), then the closed-loop system will be stable.
{\hfill \ensuremath{\blacksquare}}

\subsection{Initializing Controller}
For the given structure in Figure.~\ref{fig:damping_loop}, it remains to be shown how to select the initial stabilizing controllers in order to guarantee the stability of the closed-loop system. From the control structure of the power converter control system, it can be observed that if all the gains in Figure.~\ref{fig:damping_loop} are set to zero, then the system will be in open-loop. However, since $G \in \mathscr{S}$, then selecting $k_0 = 0$ will guarentee the stability of the closed-loop system.

If the initializing controllers are selected such that the performance with these controllers is far from the desired performance, then it is possible that either the optimization problem yields no feasible solution, or that the solver runs into numerical problems (which leads to infeasible solutions). One method to resolve this problem is to apply relaxation techniques where a relaxed optimization problem is solved; the solution to the relaxed problem can then be used as the initializing controllers for the non-relaxed problem.

\subsection{Convex Optimization via Semi-Definite Programming}
All of the optimization problems considered in section \ref{sec:loop_shape} are known as semi-infinite programming (SIP) problems since there are a finite number of optimization variables $k$ and an infinite number of constraints with respect to $\omega$. To solve any of these problems, the optimization algorithm can be converted to a semi-definite programming (SDP) problem. In this manner, a predefined frequency grid can be implemented in order to solve a finite number of constraints. In other words, for a finite number of frequency points $n$ selected in $\omega \in [0,\infty)$, then $n$ constraints must be satisfied. This frequency grid can be predefined in a variety of manners (see \cite{GKL10b}, \cite{SVBB11}, \cite{FR05}).

@@

\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{c|c|c}
                                                                               & Value                      & Units \\ \hline
\begin{tabular}[c]{@{}c@{}}$U_0$\\ (Output Voltage)\end{tabular}               & $700$                      & V     \\ \hline
\begin{tabular}[c]{@{}c@{}}$I_0$\\ (Output Current)\end{tabular}               & $850$                      & A     \\ \hline
Input Power                                                                    & $18$                       & kV    \\ \hline
Input Frequency                                                                & $50$                       & Hz    \\ \hline
\begin{tabular}[c]{@{}c@{}}IGBT equivalent \\ switching frequency\end{tabular} & $5000$                     & Hz    \\ \hline
Transformer Weight                                                             & $4500$                     & kg    \\ \hline
Control Type                                                                   & RegFGC3 Type 10 / Ethernet \cite{CKS11} & $-$  
\end{tabular}
\end{table}

@@

\subsection{Frequency Response Measurement}
Since the proposed method uses a data-driven methodology with frequency-domain data, the FRF of each subsystem within the power converter control system must be obtained. In other words, we must obtain the FRF of $G$, $H$, $P_1$, and $P_2$. The signals that are accessible for the measurements are the inputs to the capacitor banks ($U_{dc}$ in Fig.~\ref{fig:schematic}, which is approximately equal to $v_r$ in Fig.~\ref{fig:damping_loop}), and the outputs of the sensors $P_1$ and $P_2$. Therefore, when all of the controller gains are set to zero, we are able to obtain the frequency responses of $GHP_1$ and $GP_2$. However, note that $G$ appears independently of $P_2$ in (\ref{eq:Tclp}) and (\ref{eq:Tcl}); since $P_1$ and $P_2$ are sensors with very high bandwidths relative to $G$ (approximately $10 \: kHz$), then $G \approx GP_2$  at frequencies less than $1 \: kHz$.

The frequency response of the subsystems were obtained with a transfer function analyzer (Powertek GP102) which implements a sine-sweep method that recovers the gain and phase of a system at discrete frequency points. The appropriate scaling factors were taken into account for the measurements (due to the series connection of the SATURN modules) in order to coincide with the structure used in Fig.~\ref{fig:damping_loop}. The frequency responses of $GP_2$ and $GHP_1$ are shown in Fig.~\ref{fig:G} and Fig.~\ref{fig:GHP1}, respectively.

@@

Although the delay in $G$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment. This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$ (when the system is operating in closed-loop mode). The value of the delay is uncertain and is known to be in the range of $\tau_e \in [0,30]\mu s$. Therefore, a multi-model design can be considered where the additional delay can be gridded in this range and incorporated into the closed-loop TF's. The grid was established in intervals of $5 \: \mu s$ (i.e., $\tau_{e_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).
